---
title: "Money, Happiness and the Midlife Crisis"
author: "Richard Ball"
date: 2017-03-08
output: pdf_document
---

This is an Rmarkdown document.

```{r data, echo=FALSE, results="hide"}
library("knitr")
opts_chunk$set(echo=FALSE)
library("rio")
library("ggplot2")
suppressPackageStartupMessages(library("stargazer"))
country <- rio::import("../Analysis Data/country-analysis.dta")
individual <- rio::import("../Analysis Data/individual-analysis.dta")
```

There are some descriptive statistics about the data:

```{r table1}
kable(aggregate(cbind(cm_satis, inc, exp) ~ CountryName, data = country, FUN = mean))
```

And the main regression are shown in the table.

```{r table2, results = "asis"}
stargazer(
  x1 <- lm(satis ~ age + age2, data = individual),
  x2 <- lm(satis ~ age + age2 + factor(country), data = individual),
  header = FALSE
)
```

```{r inlinenumbers, results="hide"}
ageatminsatis1 <- -coef(x1)["age"]/(2*coef(x1)["age2"])
ageatminsatis2 <- -coef(x2)["age"]/(2*coef(x2)["age2"])
```

Figures 1 and 2 show some patterns.

```{r figure1}
ggplot(country, aes(x = inc, y = cm_satis)) + 
  geom_point() + 
  geom_text(aes(label = CountryName))
```

```{r figure2}
ggplot(country, aes(x = exp, y = cm_satis)) + 
  geom_point() + 
  geom_text(aes(label = CountryName))
```
  
To summarize, here are some main results. To summarize, here are some main results. The estimated minimum SWB without country fixed effects is `r ageatminsatis1`. By contrast, the estimated minimum SWB with country fixed effects is `r ageatminsatis2`.
